% This letter was sent to the First Nonprofit Corporation when acquiring
% insurance.
\documentclass[letterhead,nogit]{synhak}
\usepackage{alltt}
\begin{document}
\title{}
\maketitle

This letter confirms that a waiver of liability and release form has been
secured from all current members. All visitors and future members will be
required to do the same.

Additionally, we confirm that personal protective equipment is available to all
and worn when appropriate. Our facility rules are clearly posted in multiple
locations around the space and are included for reference:

\begin{enumerate}
\item Be excellent to each other.
\item Wear proper safety equipment.
\item If you don't know how to use it, you can't use it.
\item Keep it tidy.
\item If it is not yours, don't break it.
\item If its broken, fix it.
\end{enumerate}

-- Trever Fischer, Champion, Board Member

\begin{alltt}
-----BEGIN PGP MESSAGE-----
Version: GnuPG v1.4.12 (GNU/Linux)

owFNkr2LFEEQxcf1AxzQu8XEsMDgUJeNxOAwuUMEuUADweQEe3pqnGJ7usfq7p0b
DhGNNBAUDE4T/TcEw8PEyEDQ2EjzS8Xq2VvZsKvqvfm9mnp97mQ2Gl8/3/09XLt8
cOLr7yK7+/6bvleTB4MhIIN2tiJuPIRaBVDQKZpL2VVgSBVkKPSgbAmMBpVHqBw3
UCsPBaLNPerIWELFrgFlDMiT0QZosCmQ/RS2pDgnT8GxH4yqGESyHICOZKDAnPFx
pGQVHJROaBC8anCa51tlSYGcFft+Ah0ukRfErZikHrTsAuog9JCs2iZhSE41V2RU
YTA5i0eeIDrHFroaLahWhC2TCjiFO5GhUnqRmqNBkQurluhsemidD0JIFppoArUG
c+O0SnBp0EVxHsBbpXEIm9RktYllWpJjWWOFsiCNm3m+W+AjsvtoY4Ms33+S71LA
BrYlwZ5GY1ICgUala3BizNPjifvCkwJLeNlShUL7P/Ny5nYFvYuyS7sRYGZdB7Xr
Xia/KL+RwmRoa5Xai8pSuYPYyhMClf2KGw3rtC4kIfvJsXXBqGYr6mFSzoPdDO0E
KtpbNNGWq1Ff3DqVjUfZmdOjdJFZfnZ9eaZHf7KPBxeuXHwIzzeO3q4dXn22/v3N
zk3MPmz/+Hzj0v7Pa+ETvnr67sGvcftl8x8=
=MoOM
-----END PGP MESSAGE-----
\end{alltt}

\end{document}
