\documentclass{synhak}
\usepackage{questions}

\begin{document}
\title{Equipment Checkout Policy}
\maketitle

The Equipment Checkout Policy is designed to ensure that equipment and tools are
as broadly available as possible without limiting loan periods too much, provide
priority cases for classes, and to make sure equipment remains in good working
order.

\begin{enumerate}
\item SYNHAK equipment may be checked out at the discretion of a SYNHAK Champion.
\item A SYNHAK membership in good standing is required for checking out
equipment.
\item An up to date SYNHAK member contact form is required.
\item The minimum age for checking out equipment is 18 earth years of age.
\item All equipment must be checked out in person.
\item Equipment loan periods may not extend fourteen days.
\item You are responsible for returning all equipment by the due-date issued at
the time of checkout.
\item You may request a renewal at the discretion of a SYNHAK Champion.
\item Items may only be renewed by phone or in person, as availability must be
confirmed prior to renewing.
\item When you check something out, you assume personal financial responsibility
for the loss or damage of items.
\item Late returns may be subject to fines. Failure to pay fines may result in
termination of membership.
\item Lost, broken, or stolen equipment will be subject to replacement and
processing costs.
\item If your SYNHAK membership is terminated or suspended at any time, any and
all checked out equipment must be returned immediately.
\end{enumerate}

I, \Qline{8cm}, have fully read and understand the above terms and conditions. I
fully assume all risks and responsibilities associated with use of the equipment.

\begin{spacing}{3.5}
\Qq{Signature} \Qline{10cm}

\Qq{Printed Name} \Qline{8cm} \Qq{Date} \Qline{2cm}
\end{spacing}

\end{document}
