\documentclass{synhak}
\begin{document}
\title{SYNHAK Last Out Procedure}
\maketitle

\begin{Large}
Welcome to SYNHAK.  If you are the last one out of the space, please help us out by making sure that all of the following things are taken care of.
\end{Large}

\begin{itemize}
\item Ensure that all power tools are off and unplugged.  Some commonly used items that should be checked are:
\begin{itemize}
\item The Electronics Lab's soldering station, oscilloscope, power supply, etc
\item The Tool Room's saws, drills, grinders, welder, etc
\item Computers, projector, and anything else that consumes power that isn't required to be on at all times
\end{itemize}
\item Turn off all lights.  The light switches are as follows:
\begin{itemize}
\item Main Shop Lights: On the wall directly adjacent to our main 4' door to the left of the door across the hall
\item Tool Room Lights: Immediately inside the tool room, on the left
\item Classroom Lights: First switch is immediately inside the classroom, to the left.  Second switch is in the next room in, on the right.
\end{itemize}
\item Ensure that all compressed-gas tanks are turned off.  Propane, oxy-acetylene, MAPP gas, etc
\item Ensure that all messes that you have made are cleaned up.
\item Ensure that the classroom is locked, handle and deadbolt.  The key is kept on the orange tool rack next to the pinball machine attached to a large wooden fork.
\item Ensure that the main shop door is locked.  Press the button and rotate to lock.
\item Check that all overhead doors throughout the building are closed and secured.
\item Make sure the lights throughout the rest of the building are off, including the bathroom.
\item Close and lock whichever door you entered through.
\item If you are unsure of what to do, ask a Champion.
\end{itemize}

\end{document}
