\documentclass[letterhead,nogit]{synhak}
\usepackage{alltt}
\usepackage{multicol}
\begin{document}
\title{}
\maketitle
SYN/HAK provides an environment for people to educate, create, and share amongst
themselves and
others within the domains of technology, art and science.

% Copy-pasted from devin's email. Needs fixed indentation :E
Through talks, classes, workshops, collaborative projects, and other activities, to
encourage research,
knowledge exchange, learning, and mentoring in a safe, clean space
Provide educational spaces for teaching practical skills and theory of technology,
science, and art.
Provide work space, storage, and other resources for projects related to art,
science, and technology
that will benefit the individual members' personal growth in their fields of
interest, encouraging the
individual members to share their projects and knowledge for the betterment of
society through art,
science, and technology.
To create, learn, and teach, individually and as a group, inviting members of the
community in the
Akron area and the world.
To develop, support the development of, and provide resources for the development of
free and open
source software and hardware for the benefit of society.
Collaboration across disciplines for the benefit of cultural, charitable, and
scientific causes.
To foster, by all legal means, the common purposes of its participants
To conduct or engage in all lawful activities in furtherance of the stated purposes
or those incidental to them.

    We are currently seeking donations of anything they may improve our efforts to
educate, create, and share to our members and the public.

\begin{multicols}{2}
\begin{itemize}
\item Tables
\item Chairs
\item Desks
\item Office equipment
\item Work benches
\item Kitchen fixtures and equipment
\item Cabinets
\item Tools
\item Wood working equipment
\item Metal working equipment
\item Storage racking and shelves
\item Electronic tools and equipment
\end{itemize}
\end{multicols}

\end{document}
